### 2025-11-15 sections/2-methods.tex
couple more typos

\subsubsection{Repeated \texorpdfstring{$\rho$}{p}-NN}
\label{sec:methods:knn-search:repeated-rnn}
This algorithm repeats parts of $\rho$-NN search~\cite{ishaq2019clustered}, which finds all points within a radius $\rho$ around a query.
Repeated $\rho$-NN begins by using \textsc{TreeSearch} (Alg~\ref{alg:methods:rnn-search:tree-search}) on the root cluster $\mathcal{R}$ with the search radius $r$ equal to the radius of $\mathcal{R}$ divided by $|\textbf{X}|$.
If the returned set $\mathcal{Q}$ is empty, we double $r$ and repeat \textsc{TreeSearch} until $\mathcal{Q}$ is non-empty.
Now, so long as $\sum_{\mathcal{C} \in \mathcal{Q}} |\mathcal{C}| < k$, we repeat \textsc{TreeSearch}, but instead of doubling $r$, we multiply it by a factor determined by the LFD in the vicinity of the query ball.
In particular, we increase the radius by a factor of $\big( {\frac{k}{\sum_{\mathcal{C} \in \mathcal{Q}} |\mathcal{C}|}} \big)^\frac{1}{\mu}$,
where $\mu$ is the harmonic mean of the LFD of the clusters in $\mathcal{Q}$, to ensure that this factor is not dominated by outlier clusters with very high LFD.
Intuitively, this factor will be large when we have found few points or the LFD is low, because in these cases, we can afford to increase the radius quickly. It will be small when we have found almost all $k$ points or LFD is large, and thus we want to increase the radius slowly.
Once $\sum_{\mathcal{C} \in \mathcal{Q}} |\mathcal{C}| \geq k$, we perform \textsc{LeafSearch} (Alg~\ref{alg:methods:rnn-search:leaf-search}) to find the $k$ nearest neighbors.
\vspace{-0.1in}
\begin{algorithm}[h]
    \caption{\textsc{TreeSearch}($\mathcal{C}$, $q$, $r$)}
    \label{alg:methods:rnn-search:tree-search}
    \begin{algorithmic}
        \Require $\mathcal{C}$, a cluster
        \Require $q$, a query
        \Require $r$, a search radius
        \If{$\delta^+_\mathcal{C} \leq r$}
            \State \textbf{return} $\{\mathcal{C}\}$
        \EndIf
        \State $[\mathcal{L}, \mathcal{R}]$ $\Leftarrow$ \textit{children} of $\mathcal{C}$
        \State \textbf{return} \Call{TreeSearch}{$\mathcal{L}, q, r$} $\cup$ \Call{TreeSearch}{$\mathcal{R}, q, r$}
    \end{algorithmic}
\end{algorithm}
\vspace{-0.2in}

>>>>

\subsubsection{Repeated \texorpdfstring{$\rho$}{p}-NN}
\label{sec:methods:knn-search:repeated-rnn}
This algorithm builds on $\rho$-NN search from CHESS~\cite{ishaq2019clustered}, which finds all points within a radius $\rho$ around a query.
Repeated $\rho$-NN begins by using \textsc{TreeSearch} (Alg~\ref{alg:methods:rnn-search:tree-search}) on the root cluster $\mathcal{R}$ with the search radius $r$ equal to the radius of $\mathcal{R}$ divided by $|\textbf{X}|$.
If the returned set $\mathcal{Q}$ is empty, we double $r$ and repeat \textsc{TreeSearch} until $\mathcal{Q}$ is non-empty.
Now, so long as $\sum_{\mathcal{C} \in \mathcal{Q}} |\mathcal{C}| < k$, we repeat \textsc{TreeSearch}, but instead of doubling $r$, we multiply it by a factor determined by the LFD in the vicinity of the query ball.
In particular, we increase the radius by a factor of $\big( {\frac{k}{\sum_{\mathcal{C} \in \mathcal{Q}} |\mathcal{C}|}} \big)^\frac{1}{\mu}$,
where $\mu$ is the harmonic mean of the LFD of the clusters in $\mathcal{Q}$, to ensure that this factor is not dominated by outlier clusters with very high LFD.
Intuitively, this factor will be large when we have found few points or the LFD is low, because in these cases, we can afford to increase the radius quickly. It will be small when we have found almost all $k$ points or LFD is large, and thus we want to increase the radius slowly.
Once $\sum_{\mathcal{C} \in \mathcal{Q}} |\mathcal{C}| \geq k$, we perform \textsc{LeafSearch} (Alg~\ref{alg:methods:rnn-search:leaf-search}) to find the $k$ nearest neighbors.
\vspace{-0.075in}
\begin{algorithm}[h]
    \caption{\textsc{TreeSearch}($\mathcal{C}$, $q$, $r$)}
    \label{alg:methods:rnn-search:tree-search}
    \begin{algorithmic}
        \Require $\mathcal{C}$, a cluster
        \Require $q$, a query
        \Require $r$, a search radius
        \If{$\delta^+_\mathcal{C} \leq r$}
            \State \textbf{return} $\{\mathcal{C}\}$
        \EndIf
        \State $[\mathcal{L}, \mathcal{R}]$ $\Leftarrow$ \textit{children} of $\mathcal{C}$
        \State \textbf{return} \Call{TreeSearch}{$\mathcal{L}, q, r$} $\cup$ \Call{TreeSearch}{$\mathcal{R}, q, r$}
    \end{algorithmic}
\end{algorithm}
\vspace{-0.225in}

### 2025-11-15 sections/3-datasets.tex
couple more typos

    \caption{Local fractal dimension vs. cluster depth across six datasets;
    note the different y-axes.
    The x-axis is tree depth;
    the y-axis is the LFD of clusters at that depth.
    We plot the 5th, 25th, 50th, 75th, and 95th percentiles, and min/max.
    The Fashion-MNIST, Glove-25, Sift and Silva datasets are real-world datasets and exhibit low LFD, indicating a manifold structure.
    The Random dataset has high LFD, indicating lack of manifold structure.
    The measured LFD of ``only'' 20 is a consequence of Equation~\ref{eq:methods:lfd-original} and only having sampled $10^6$ points in a 128-dimensional space $(\log_2 10^6 \approx 20)$;
    We would need to sample many more points ($>2^{128}$), for the LFD to approach the embedding dimension of 128.
    The RadioML dataset is also a randomly generated dataset, but with a much more elaborate generation process.
    It exhibits behavior akin to the Random dataset across three separate radial scales, as indicated by the distinct peaks in LFD at different depths.}
    \label{fig:results:lfd-plots}
\end{figure}

>>>>

    \caption{Local fractal dimension vs. cluster depth across six datasets;
    note the different y-axes.
    The x-axis is tree depth;
    the y-axis is the LFD of clusters at that depth.
    We plot the 5th, 25th, 50th, 75th, and 95th percentiles, and min/max.
    The Fashion-MNIST, Glove-25, Sift and Silva datasets are real-world datasets and exhibit low LFD, indicating a manifold structure.
    The Random dataset has high LFD, indicating lack of manifold structure.
    Its measured LFD of ``only'' 20 is a consequence of Equation~\ref{eq:methods:lfd-original} and having sampled only $10^6$ points in a 128-dimensional space $(\log_2 10^6 \approx 20)$.
    We would need to sample many more points ($>2^{128}$), for the LFD to approach the embedding dimension of 128.
    The RadioML dataset is also a randomly generated dataset, but with a much more elaborate generation process.
    It exhibits behavior akin to the Random dataset across three separate radial scales, as indicated by the distinct peaks in LFD at different depths.}
    \label{fig:results:lfd-plots}
\end{figure}
